\phantomsection\addcontentsline{toc}{section}{Références}

\begin{thebibliography}{ABC}	
    %\bibitem[REF]{reference} auteur. \emph{titre}. édition, année.
    %\bibitem[LPP]{lpp} Rolland. \emph{LaTeX par la pratique}. O'Reilly, 1999.
    
    \bibitem{william92}
       William H. Press, Brian P. Flannery.
      \emph{Numerical Recipes in C: The Art of Scientific Computing}.
      Cambridge University Press.
      2 edition.
      October 30, 1992.
    
    \bibitem{coulais10}
       Coulais, A.; Schellens, M.; Gales, J.; Arabas, S.; Boquien, M.; Chanial, P.; Messmer, P.; Fillmore, D.; Poplawski, O.; Maret, S.; Marchal, G.; Galmiche, N.; Mermet, T.
       \emph{Status of GDL - GNU Data Language}.
       434, Astronomical Data Analysis Software and Systems XIX.
       2010.
       \url{http://www.aspbooks.org/publications/434/187.pdf}
    
    \bibitem{coulais12}
       Coulais, A.; Schellens, M.; Arabas, S.; Lenoir, M.; Noreskal, L.; Erard, S.
       \emph{Space Missions: Long Term Preservation of IDL-based Software using GDL}.
       461, Astronomical Data Analysis Software and Systems XXI.
       2012.
       \url{http://www.aspbooks.org/publications/461/615.pdf}
    
    \bibitem{bilan10}
       \emph{Bilan Social}.
       L'Observatoire de Paris.
       Septembre 2010.
    
    \bibitem{rapport10}
       \emph{Rapport d’Évaluation de l’Observatoire de Paris}.
       Agence d’Évaluation de la Recherche et de l'Enseignement Supérieur.
       Mars 2010.
       \url{http://www.aeres-evaluation.fr/content/download/13342/186416/ffile/aeres-s1-obsparis.pdf}
    
    \bibitem{docgdl}
       Sylwester Arabas, Alain Coulais.
       \emph{Documentation de GDL}.
       Marc Schellens and The GDL team.
       Janvier 3, 2012.
       \url{http://gnudatalanguage.sourceforge.net/gdl.pdf}
    
    \bibitem{docidl}
       \emph{Documentation d'IDL}.
       \url{http://www.exelisvis.com/docs/}
    
    \bibitem{doceig}
       \emph{Documentation d'Eigen}.
       \url{http://eigen.tuxfamily.org/dox/}
    
    \bibitem{dio}
       \emph{Description de matériels de l'Observaoire de Paris}.
       \url{http://dio.obspm.fr}
    
    \bibitem{wiki}
       \emph{Les divers articles}.
       \url{http://wikipedia.org}
    
\end{thebibliography}
